\chapter{INTRODUCTION AND LITERATURE SURVEY}
This part includes the whole overview towards our project, platforms used and programming languages used.
\section{INTRODUCTION}
In this era we are able to see very high technical advancements and automation's in the industrial sector.The growth of the technology has made many changes in the lives of the people.These things have impacted a lot on the industrial sector mainly to reduce the cost of the production, this implementation has made changes in employment sector and reduced the number of labour day by day. The objective of our project also prefers for the automation of the industries and include maintenance of the health condition of the machines. Using the sensors such as Bluetooth module, sound sensors we analyze the condition of the machines.This is very important because the industries spend lot of money for the maintenance of their machine's. In some conditions industries work is going to stop because of the damaged machines. The machines could have been stopped from being damaged with some proper observations. In our cases we have taken sound and distance as  parameters to analyze the health condition of the machine by these small changes industries can avoid huge losses. Previously many industries have their employees for the observation of the machines which makes the companies to bear a high labour cost. By our objective we have tried to solve these issues as we have came across. We have taken this topic by understanding the real world situations that have made greater impact, mainly the industrial factors made the consequences difficult to understand and  takes lot of time to solve them. All the industrial applications are difficult to analyze in their early stages and it takes lot of time to fix the issue. The cost estimation becomes easy for the industries to spend with our application, industries can be well prepared before any damage could occur. It becomes easier for the industries to make the economical planning properly to spend on the damaged machines. Our major objective also support this context as we making low cost IoT application which can be helpful to decrease the economical loss to the industries. Application consist some of the sensors such as vibration sensor, ultrasonic sensor, sound sensor are used in our application to make it more feasible and cost effective we have used them on the Arduino platform, which is more easy to use, easy to handle platform while implementing the IoT applications. Each part of the application behaves as a source, destination and intermediate node. 


     
\subsection{ Mode of communication}
In our IoT application we use wireless communication between Bluetooth to Bluetooth using serial port data transmission by fixing a sensor on the Arduino board and transmitting the input through Bluetooth modules. 
So each node in the system can behave as:
\begin{enumerate}[(a)]
 \item Source
 \item Destination
 \item Intermediate nodes
\end{enumerate}
Here we get to transmit the information from one node to another node tends to involve in the data transmission.  

\subsubsection{Related Definitions}
\begin{enumerate}[(i)]
 \item {\bf Internet of things:} Physical system with sensor fixed on platform to exchange the data.
 \item {\bf wireless sensor networks:}The transmission of the  $r$.
 \item {\bf Serial data transmission:} Sending of a single bit sequentially over communication channel.
 
\end{enumerate}
\citet{edtr7}.

\section{ARDUINO } 
{\bf Key Features} \\
- easy to use . \\
- easy to fix any sensor and take the input. \\
- Supports Arduino programming languages based on processing . \\
 \\\
{\bf Version} - Arduino uno (2017)
\section {Thinkspeak}
We are using the cloud platform thinkspeak for our real time data storage, to store the data and hold a threshold value at which we can identify the variation in parameter and detect the damage to the machine caused by different factors.\\\
\\\
{\bf Key Features} \\
-Provides individual and shared account for data storage. \\
-Secure in data storage. \\
-Makes easy to access the data stored in cloud.\\
\\\
{\bf version}  -think speak (2017)
\section{LITERATURE REVIEW}
We deal with three main literature's majorly from IoT applications, wireless sensor networks and cloud.

IoT applications have made an huge impact on the growth of the technology and it has many hardware applications we are able see, as they are becoming highly simple and compact in the nature, these applications gathers all the real time data which in term help to analyze the problem. With the available real time data there are many huge applications which have made a huge impact on the human life, growing technology also has brought many technology such as machine learning and artificial intelligence.

 There are principle associated with this wireless sensor networks, but with this technology many changes and growth of new products arrived with this technology, the main part that it reduces the wires and cost associated with that which in turn a good option for the people who don't want those wires around them, this says about the quality of the technology. Based on the studies, wireless senor network is one of the major topic where many research are going on.
The objective we are going with also involve the same contexts which will have a huge impact on the industrial processes and minimizing their cost of the production. 

By using many sensor we have considered many parameters such as temperature, vibration, sound and different parameters which affect the machines. In our major part of the implementation we consider the inputs from these and involve many other consequences with these and analyze them and fix a threshold value which will help us to understand problem when it crosses certain values and we get information that some of the machines has been damaged which further can be solved.

In this field important work done by the cloud part which will help us to store the data and manage to identify and fix certain threshold value which becomes easy for the system to analyze the input data from the sensors and collecting data over a period of time which gives us ample of time to asses the error in in the system. Major help from this cloud storage which will help us to access the data from everywhere and as it is fully secured.

This project we will be testing in electric room where we will test the the problem with the central AC from which we will get different sound by which we can identify the problems in the system. 
In this many consequences come into existence such as external parameters as sound from other sources will have impact on the input we are selecting  which will be directly stored in the cloud this can make huge error in the output we are predicting, there are many human and environmental problems have impact on our objective. 

Considering all these issues our objective has made lot of changes due to external factors which we have discusses previously. Another main issue is with the cloud data security which can be modified with malwares which will have an direct impact on our results as our objective can be integrated in any industry with machinery maintenance part which will be directly helping us to improve the quality of the industrial maintenance process.
\section{OBJECTIVE}
The main objective is to design low cost hardware IoT Application for industrial process.
To achieve this goal the fallowing objectives are set \\
1.To design a multi sensor based device for data acquisition.\\
2.Connect different multi sensor based data acquisition board through an energy efficient communication scheme.\\
3.To design data acquisitions scheme to collect real life data from different deployed multi sensor based data acquisition board.\\
4.To design a scheme to analyze the collected data for identification of fault of the industrial machine.\\
